%%____________________________________________________________________________||
\section{Summary}
\label{sec:conclusions}
Searches for new physics by the CMS collaboration are performed using a wide variety of 
strategies and using events with different final states and kinematic properties. 
Re-interpreting these searches requires approximating the background model
and associated systematic uncertainties for the search. This can be 
achieved by defining a simplified likelihood combining one or more search regions in which the systematic 
uncertainties on the backgrounds are modelled  as Gaussian  constrained nuisance parameters. 
To define the simplified likelihood requires only the observed data and the total expected background in each search region, observed data, 
total expected background contributions and the covariance matrix describing the covariance of the total background between each of the search regions. 
In addition, the number of search regions being considered can be reduced, where necessary, through the use of aggregated search regions. 
A toy example search has been used to demonstrate and validate the use of the simplified likelihood and aggregated search 
regions. Some examples of where the simplified likelihood does not provide a good approximation of the 
full likelihood used by CMS searches have been highlighted. Using only the reduced set of information required by the simplified likelihood 
approach allows for re-interpretation of public CMS searches under different BSM physics models, where the conditions stipulated for the 
method are met.

%%____________________________________________________________________________||
